%---------------------------------------------------
% Nombre: bibliografia.tex  
% 
% Bibliografia
%---------------------------------------------------

\begin{thebibliography}{99}

\bibitem{clustering}
	\emph{} Juan Carlos Cubero y Amparo Vila Miranda. Clustering. \textit{Transparencias de clase de teoría}. 2017-2018.

\bibitem{anomalias}
	\emph{} Juan Carlos Cubero. Detección de anomalías. \textit{Transparencias de clase de teoría}. 2017-2018. 
	
\bibitem{reglas}
	\emph{} Jesús Alcalá Fernández. Reglas de Asociación: Introducción. \textit{Transparencias de clase de teoría}. 2017-2018. 

\bibitem{kmeans}
	\emph{} MacQueen, J. Some methods for classification and analysis of multivariate observations. \textit{Proceedings of the Fifth Berkeley Symposium on Mathematical Statistics and Probability}, Volume 1: Statistics, 281-297

\bibitem{dbscan}
	\emph{}Martin Ester, Hans-Peter Kriegel, Jörg Sander, and Xiaowei Xu. 1996. A density-based algorithm for discovering clusters a density-based algorithm for discovering clusters in large spatial databases with noise. In \textit{Proceedings of the Second International Conference on Knowledge Discovery and Data Mining (KDD'96)} .226-231.

\bibitem{BIRCH}
	\emph{} Zhang, T.; Ramakrishnan, R.; Livny, M. (1996). "BIRCH: an efficient data clustering method for very large databases". \textit{Proceedings of the 1996 ACM SIGMOD international conference on Management of data - SIGMOD '96}. pp. 103-114

\bibitem{CURE}
	\emph{} Guha, Sudipto; Rastogi, Rajeev; Shim, Kyuseok (2001). "CURE: An Efficient Clustering Algorithm for Large Databases". \textit{Information Systems. 26}: 35?58

\bibitem{ROCK}
	\emph{} S. Guha, R. Rastogi and K. Shim, "ROCK: a robust clustering algorithm for categorical attributes," \textit{Proceedings 15th International Conference on Data Engineering }, Sydney, NSW, 1999, pp. 512-521.

\bibitem{CLARANS}
	\emph{} R. T. Ng and Jiawei Han, "CLARANS: a method for clustering objects for spatial data mining," in  \textit{IEEE Transactions on Knowledge and Data Engineering}, vol. 14, no. 5, pp. 1003-1016, Sep/Oct 2002.


\bibitem{clustering2}
	\emph{}Tan, Steinbach, Kumar. Introduction to Data Mining, chapter 8: Cluster Analysis: Basic Concepts and Algorithms. 

\bibitem{com}
	\emph{}Moosavi, S.A. and Jalali, M. Community detection in online social networks using actions of users. 2014 \textit{Iranian Conference on Intelligent Systems, ICIS}

\bibitem{mkt}
	\emph{}Baier D., Daniel I.  Image Clustering for Marketing Purposes. In: Gaul W., Geyer-Schulz A., Schmidt-Thieme L., Kunze J.  \textit{Studies in Classification, Data Analysis, and Knowledge Organization}. Springer, Berlin, Heidelberg. 2012. 
	
\bibitem{anomalias2}
	\emph{}Charu C. Aggarwal. 2013. Outlier Analysis. Springer Publishing Company, Incorporated.

\bibitem{fmeasure}
	\emph{}  Kaggle Wiki \url {https://www.kaggle.com/wiki/MeanFScore}
\bibitem{bitcoin}
	\emph{}Prado-Romero M.A., Doerr C., Gago-Alonso A. (2018) Discovering Bitcoin Mixing Using Anomaly Detection. In: Mendoza M., Velastín S. \textit{Progress in Pattern Recognition, Image Analysis, Computer Vision, and Applications. CIARP 2017}. Lecture Notes in Computer Science, vol 10657

\bibitem{mailserver}
	\emph{}Zacher, S. \& Ryba, P. (2018). Anomaly detection in server metrics with use of one-sided median algorithm. \textit{Journal of Applied Computer Science Methods}, 9(1), pp. 5-2
	

\bibitem{agrawal}
	\emph{}Rakesh Agrawal, Tomasz Imieliski, and Arun Swami. Mining association rules between sets of items in large databases. \textit{SIGMOD} Rec. 22, 1993, 207-216. 
	

\bibitem{apriori}
	\emph{} R. Agrawal and R. Srikant Fast algorithms for mining association rules in large databases. 1994. \textit{Proceedings of the 20th International Conference on Very Large Data Bases}, VLDB, pp. 487-499.
	
\bibitem{eclat}
	\emph{} Zaki, M. J., Parthasarathy, S., Ogihara, M., \& Li, W. (1997, August). New Algorithms for Fast Discovery of Association Rules. In \textit{KDD} (Vol. 97, pp. 283-286).	
		
	
\bibitem{fpg}
	\emph{} Han, J., Pei, H., Yin, Y.: Mining Frequent Patterns without Candidate Generation. 2000. \textit{Proc. Conf. on the Management of Data} (SIGMOD 2000), Dallas, TX, pp. 1?12.			
		
\bibitem{pollutants}
	\emph{}HU, Q. L., \& GUO, S. (2017). Mining on the Air Pollutants Association Rules of Lan-Xi-Yin Urban Agglomeration. DEStech Transactions on Environment, Energy and Earth Sciences, (epee)		
	

\bibitem{basket}
	\emph{}Zhong, X. A Study on Basketball Techniques and Tactics Based on Apriori Algorithm. Wireless Personal Communications, 1-10.	
	
\end{thebibliography}
%---------------------------------------------------